### 2018-02-03 metrics.tex
did some cleaning

>>>>

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{figures/pdf/figure-01}
    \caption{\textbf{(a)} Region of interest used by \citet{Taborda_2014_BSSA} for the simulations of the 2008 $M_W ~ 5.4$ Chino Hills earthquake, including the epicenter, focal mechanism, and major quaternary faults. In the background, the main roads and topography are shown for visual reference. \textbf{(b)} Distribution of the 336 stations (gray dots) used by \citet{Taborda_2014_BSSA} for the validation analysis of their simulations within the modeling domain shown in part (a). Roads, city names, and the hillshade topography are also shown here in the background for reference. The color version of this figure is available only in the electronic edition.}
    \label{fig:chino-hills}
\end{figure*}

### 2018-02-03 results.tex
did some cleaning

>>>>

\begin{figure*}[t]
	\centering
	\includegraphics[width=\textwidth]{figures/pdf/figure-05}
	\caption{A sample of the results from the multi-dimensional clustering analysis for pairs of consecutive metrics C1 through C11. These results are part of the 55 possible sub-spaces with 2 features (metrics). The cluster centers are shown with a cross symbol. Although for some pairs it may be obvious, the clusters 1 through 4 do not necessarily correspond in that order to the validation classes poor, fair, good, and excellent. The color version of this figure is available only in the electronic edition.}
	\label{fig:clusters-sample}
\end{figure*}
